Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-03-07 demystify.tex
updates

In my personal opinion, highlighting URM or LBGTQ+ identity can \emph{indeed be beneficial}, especially if you can articulate how your diverse experiences contribute to diversity and inclusion in academic.  Many universities have a strong commitment to diversity and inclusion and actively 
\emph{recruit students from underepresentative backgrounds} (e.g., some \href{https://cse-climate.engin.umich.edu/reports/climate-dei-reports/cse-climate-and-dei-report-2022-2023/#grad-ethnicity}{stats from UMich CSE} and \href{https://www.gmu.edu/news/2022-09/mason-now-top-10-public-university-diversity-innovation-and-cybersecurity-education-us}{GMU} often promotes itself as one of the most diverse universities in the US). Moreover, many scholarships and fellowships specifically for URM and LBGTQ+ students, which applicants should explore if qualify.

It is understandable that some applicants might feel uncomfortable disclosing this, fearing they would lost a chance of working with a faculty with bias.  However, if someone has such an issue, then you might not want to work with them anyway (and such bias is not acceptable in academic and likely would not be tolerated by the university). In my experience, it is the opposite: \emph{many profs. actively seek out to work with students from diverse backgrounds and view diversity as an asset to their research group}.

Moreover, promoting diversity aligns with the broadening participation in computing (BPC) goal within academia (e.g., see the \href{https://plans.bpcnet.org/GeorgeMasonUniversity_ComputerScience_DepartmentalBPCPlan.pdf}{BPC plan at GMU CS}) and government funding agencies such as NSF (e.g., see \href{https://new.nsf.gov/cise/broadening-participation}{here} and \href{https://www.nsf.gov/pubs/2022/nsf22125/nsf22125.jsp}{here}). 
Also, sometimes providing this information can make it easier for faculty to apply for certain scholarships or fellowships to support you, e.g., from a private donor that has offered a fellowship only to students from certain background.

Ultimately, this is a personal choice and you do what make you feel comfortable. Seeking guidance from your close professors and collaborators is a good idea. However, it is important to recognize that diversity is strongly valued and celebrated within CS programs in the US, and that you should feel empowered to share your unique experiences and perspectives.

>>>>

In my personal opinion, highlighting URM or LBGTQ+ identity can \emph{indeed be beneficial}, especially if you can articulate how your diverse experiences contribute to diversity and inclusion in academic.  Many universities have a strong commitment to diversity and inclusion and actively 
\emph{recruit students from underepresentative backgrounds} (e.g., some \href{https://cse-climate.engin.umich.edu/reports/climate-dei-reports/cse-climate-and-dei-report-2022-2023/#grad-ethnicity}{stats from UMich CSE} and \href{https://www.gmu.edu/news/2022-09/mason-now-top-10-public-university-diversity-innovation-and-cybersecurity-education-us}{GMU} often promotes itself as one of the most diverse universities in the US). Moreover, many scholarships and fellowships are created specifically for URM and LBGTQ+ students, which you should explore if qualify.

It is understandable that you might feel uncomfortable disclosing this, fearing you would lost a chance of working with a faculty who might have a bias.  However, if someone has this issue, then you might not want to work with them anyway (and such bias is not acceptable in academic and likely would not be tolerated by the university). In my experience, it is the opposite: \emph{many profs. actively seek out to work with students from diverse backgrounds and view diversity as an asset to their research group}.

Moreover, promoting diversity aligns with the goal of broadening participation in computing (BPC) that is strongly supported within academia (e.g., see the \href{https://plans.bpcnet.org/GeorgeMasonUniversity_ComputerScience_DepartmentalBPCPlan.pdf}{BPC plan at GMU CS}) and government funding agencies such as NSF (e.g., see \href{https://new.nsf.gov/cise/broadening-participation}{here} and \href{https://www.nsf.gov/pubs/2022/nsf22125/nsf22125.jsp}{here}). 
Also, sometimes providing this information can make it easier for faculty to apply for certain scholarships or fellowships to support you, e.g., from a private donor that has offered a fellowship only to students from certain background.

Ultimately, this is a personal choice and you do what you feel comfortable. Seeking guidance from your close professors and collaborators is a good idea. However, it is important to recognize that diversity is strongly valued and celebrated within CS programs in the US, and that you should feel empowered to share your unique experiences and perspectives.
